---
title: "Daily Reallocation of Sleep Stages and Affect"
author: Flora (flora.le@monash.edu)
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: no
    toc_float: no
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    number_sections: true
---

This file presents the full 
daily reallocation of sleep stages and affect
results using the
Bayesian compositional multilevel substitution analysis
for the manuscript:
Daily Reallocations of Time between Sleep Architecture and Affect: 
Insights from Bayesian Multilevel Compositional Data Analysis.

```{r, echo=FALSE, message=FALSE}
source("sleep-affect-results-out.R")
```

# Statistics for 30-minute Reallocations

 * Reallocation of 30 minutes between sleep stages and high arousal positive affect
 
```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(affect_sub_list[[1]])
```

 * Reallocation of 30 minutes between sleep stages and low arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(affect_sub_list[[2]])
```

 * Reallocation of 30 minutes between sleep stages and high arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(affect_sub_list[[3]])
```

 * Reallocation of 30 minutes between sleep stages and low arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(affect_affect_sub_list[[4]])
```

# Visualisation of Reallocation from 1 to 60 minutes of Sleep Stages and Affect
## Between person Reallocation

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(sleep_affect_plot_b, print)
```

## Within person Reallocation
```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(sleep_affect_plot_w, print)
```