---
title: "Daily Reallocation of Sleep Stages and Affect"
author: Flora (flora.le@monash.edu)
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: no
    toc_float: no
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 8
    fig_height: 5
    fig_caption: yes
    number_sections: true
---

This file presents the full 
daily reallocation of sleep stages and affect
results using the
Bayesian compositional multilevel substitution analysis
for the manuscript:
**Daily, Prospective Associations between Sleep Architecture and Affect: Insights from Bayesian Multilevel Compositional Data Analysis**.

```{r, echo=FALSE, message=FALSE}
source("sleep-affect-supp.R")
```

# Statistics for 30-minute Reallocations

*Notes*. All estimates are relative to the mean sleep architecture composition at within-person level. 
TWT = total wake time in bed, Light = light sleep, SWS = slow wave sleep, REM = rapid eye movement sleep. 
* indicates 95% credible intervals not containing 0. 
Models adjusted for age, sex, race/ethnicity, subjective social status, 
body mass index, weekdays/weekend, circadian misalignment, and previous-night pre-sleep affect.

 * Estimated difference in *high arousal positive affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sleep_affect_sub_list[[1]])
```

 * Estimated difference in *low arousal positive affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(sleep_affect_sub_list[[2]])
```

 * Estimated difference in *high arousal negative affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(sleep_affect_sub_list[[3]])
```

 * Estimated difference in *low arousal negative affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(sleep_affect_sub_list[[4]])
```

# Visualisation of Reallocation from 1 to 60 minutes of Sleep Stages and Affect

*Notes*. All estimates are relative to the mean sleep architecture composition at within-person level. 
TWT = total wake time in bed, Light = light sleep, SWS = slow wave sleep, REM = rapid eye movement sleep. 
* indicates 95% credible intervals not containing 0. 
Models adjusted for age, sex, race/ethnicity, subjective social status, 
body mass index, weekdays/weekend, circadian misalignment, and previous-night pre-sleep affect.

## Between person Reallocation

```{r, warning=FALSE, echo = FALSE, fig.align='center'}
purrr::walk(sleep_affect_plot_b_supp, print)
```

## Within person Reallocation
```{r, warning=FALSE, echo = FALSE, fig.align='center'}
purrr::walk(sleep_affect_plot_w_supp, print)
```