---
title: "Supplementary materials: Daily, prospective associations between sleep architecture and affect: insights from Bayesian multilevel compositional data analysis"
author: Flora Le (flora.le@monash.edu)
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: yes
    toc_float: no
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 8
    fig_height: 5
    fig_caption: yes
    number_sections: true
---

This file presents the full 
daily reallocation of sleep stages and affect
results using the
Bayesian compositional multilevel substitution analysis
for the manuscript:
**Daily, Prospective Associations between Sleep Architecture and Affect: Insights from Bayesian Multilevel Compositional Data Analysis**.

```{r, echo=FALSE, message=FALSE}
source("sleep-affect-supp.R")
```

# Statistics for 30-minute reallocations

*Notes*. All estimates are relative to the mean sleep architecture composition. 
TWT = total wake time in bed, Light = light sleep, SWS = slow wave sleep, REM = rapid eye movement sleep. 
* indicates 95% credible intervals not containing 0. 
Models adjusted for age, sex, race/ethnicity, subjective social status, 
body mass index, weekdays/weekend, circadian misalignment, and previous-night pre-sleep affect.

 * Estimated difference in *high arousal positive affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE, fig.width=9}
kbl(sleep_affect_sub_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF7F4")
```

 * Estimated difference in *low arousal positive affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
kbl(sleep_affect_sub_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#DCD5CE")
```

 * Estimated difference in *high arousal negative affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
kbl(sleep_affect_sub_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Estimated difference in *low arousal negative affect* for reallocation of 30 minutes between sleep stages.
 
```{r, warning=FALSE, echo=FALSE}
kbl(sleep_affect_sub_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#9DB3A8")
```

# Figures for reallocations from 1 to 60 minutes

*Notes*. All estimates are relative to the mean sleep architecture composition. 
TWT = total wake time in bed, Light = light sleep, SWS = slow wave sleep, REM = rapid eye movement sleep. 
* indicates 95% credible intervals not containing 0. 
Models adjusted for age, sex, race/ethnicity, subjective social status, 
body mass index, weekdays/weekend, circadian misalignment, and previous-night pre-sleep affect.

## Between person

```{r, warning=FALSE, echo = FALSE, fig.align='center'}
purrr::walk(sleep_affect_plot_b_supp, print)
```

## Within person
```{r, warning=FALSE, echo = FALSE, fig.align='center'}
purrr::walk(sleep_affect_plot_w_supp, print)
```